Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-11-15 paper/paper.tex
Typos

A Visualization system must be fast enough to enable fast iterations; with delays of more than 500ms analysts become less effective ~\cite{liu2014effects} or even lose their flow of though if delays are more than a second~\cite{nielsen1993response}.

@@

The HCI community found that approximate visualizations can be used in exploratory data analsis~\cite{fisher2012trust, moritz2017pangloss}.
However, there is no prior work on how exposure to approximate visualizations biases the observations and insights analysts make.

@@

There are a number of techniques for communicating uncertainty using visualizations~\cite{kay2016ish, olston2002visualizing}.
However, often users often struggle to correctly interpret the uncertainty or even draw incorrect conclusions~\cite{joslyn2013decisions}.
Moreover, in many models in the real world no statistial model is available to estimate the uncertaintly so that the approximate visualizations in our study do not show uncertainties.

@@

The two visualizations participants saw were based on the same dataset about flights in the United States \footnote{\url{http://datahub.io/dataset/open-flights}}.
\figref{fig:types} shows visualizations of approximate and precise data.
Both visualizations were bar graphs, which are common in approximate query systems \cite{moritz2017pangloss}.
The y-axis varied between the two visualizations, showing either the state the flight left from or the airline the flight was operated by.
The bars were sorted in descending order so that the state or airline with the most flights is at the top.
The x-axis in both visualization was a count value.
We chose horizontal bar charts so that long labels are easier to read.
To visually separate visualizations of approximate and precise data, we colored the bars approximate visulizations orange (\figref{fig:approx}) and prcise visualizations blue (\figref{fig:precise}).

@@

We are asking three types of questions in our study with different dependent variables:
\begin{enumerate}
\item Was there a difference between the precise and approximate visualizations (categorial dependent variable)
\item Which airline or state had the most or least flights (categorical dependent variable)
\item How many flights were on a particular airline or from a particular state (interval depdendent variable)
\item Confidence in answers to the above questions (interval dependent variable)
\end{enumerate}

>>>>

A Visualization system must be fast enough to enable fast iterations; with delays of more than 500ms analysts become less effective ~\cite{liu2014effects} or even lose their flow of thought if delays are more than a second~\cite{nielsen1993response}.

@@

The HCI community found that approximate visualizations can be used in exploratory data analysis~\cite{fisher2012trust, moritz2017pangloss}.
However, there is no prior work on how exposure to approximate visualizations biases the observations and insights analysts make.

@@

There are a number of techniques for communicating uncertainty using visualizations~\cite{kay2016ish, olston2002visualizing}.
However, often users often struggle to correctly interpret the uncertainty or even draw incorrect conclusions~\cite{joslyn2013decisions}.
Moreover, in many models in the real world no statistical model is available to estimate the uncertainty so that the approximate visualizations in our study do not show uncertainties.

@@

The two visualizations participants saw were based on the same dataset about flights in the United States \footnote{\url{http://datahub.io/dataset/open-flights}}.
\figref{fig:types} shows visualizations of approximate and precise data.
Both visualizations were bar graphs, which are common in approximate query systems \cite{moritz2017pangloss}.
The y-axis varied between the two visualizations, showing either the state the flight left from or the airline the flight was operated by.
The bars were sorted in descending order so that the state or airline with the most flights is at the top.
The x-axis in both visualization was a count value.
We chose horizontal bar charts so that long labels are easier to read.
To visually separate visualizations of approximate and precise data, we colored the bars approximate visualizations orange (\figref{fig:approx}) and precise visualizations blue (\figref{fig:precise}).

@@

We are asking three types of questions in our study with different dependent variables:
\begin{enumerate}
\item Was there a difference between the precise and approximate visualizations (categorical dependent variable)
\item Which airline or state had the most or least flights (categorical dependent variable)
\item How many flights were on a particular airline or from a particular state (interval dependent variable)
\item Confidence in answers to the above questions (interval dependent variable)
\end{enumerate}
